Continuous developmental changes in word recognition support language learning across early childhood

### 2025-09-17 paper/paper.Rmd
minor tweaks

output: rticles::pnas_article

@@

#summarize by subject
d_timecourse_by_dataset_age_subj <- d_aoi |>
  filter(t_norm>-2000) |> 
  #create age bins cutoffs
  mutate(
    age_bin = cut(age, breaks = c(0,12,15,18,21,24,27,30,36,60), 
                  labels = c("<12", "12-15","15-18", "18-21", "21-24", "24-27","27-30","30-36", ">36"))
  ) |>
  #downsample t_norm to 50ms bins
  #mutate(t_norm_downsampled = round(t_norm/50)*50) |>
  group_by(dataset_name,dataset_id,subject_id,age_bin,t_norm) |> 
  #calculate proportion time spent looking at target
  summarize(
    n=n(),
    accuracy = mean(correct, na.rm=TRUE))

>>>>

output: papaja::apa6_pdf

@@

#summarize by subject
d_timecourse_by_dataset_age_subj <- d_aoi |>
  filter(t_norm>-2000) |> 
  #create age bins cutoffs
  mutate(
    age_bin = cut(age, breaks = c(0,12,15,18,21,24,27,30,36,60), 
                  labels = c("<12", "12-15","15-18", "18-21", "21-24", "24-27","27-30","30-36", ">36"))
  ) |>
  #downsample t_norm to 50ms binsv
  #mutate(t_norm_downsampled = round(t_norm/50)*50) |>
  group_by(dataset_name,dataset_id,subject_id,age_bin,t_norm) |> 
  #calculate proportion time spent looking at target
  summarize(
    n=n(),
    accuracy = mean(correct, na.rm=TRUE))
